\documentclass[11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{needspace}
\usepackage{hyperref}

% ------------------------------------------------------------------
% Page geometry (comfortable two-page layout)
% ------------------------------------------------------------------
\geometry{top=0.55in, bottom=0.5in, left=0.65in, right=0.65in}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% ------------------------------------------------------------------
% Colors, links and section styling
% ------------------------------------------------------------------
\definecolor{primary}{RGB}{31, 73, 125}
\definecolor{muted}{RGB}{90, 90, 90}
\hypersetup{colorlinks=true, urlcolor=primary, linkcolor=primary}

\titleformat{\section}{\large\bfseries\color{primary}\uppercase}{}{0pt}{}[\titlerule]
\titlespacing{\section}{0pt}{9pt}{5pt}

% Company header (name + location) -- kept together with following sub-role/bullets
\newcommand{\company}[2]{%
  \needspace{5\baselineskip}%
  \textbf{#1} \hfill \textcolor{muted}{#2}\\[3pt]
}
% Sub-role under a company (title + dates)
\newcommand{\subrole}[2]{%
  \needspace{4\baselineskip}%
  \textit{#1} \hfill \textcolor{muted}{#2}\\[3pt]
}
% Single-line role (title + dates + location) -- kept together with its bullets
\newcommand{\role}[4]{%
  \needspace{5\baselineskip}%
  \textbf{#1} \hfill \textbf{#3} \\[2pt]
  \textit{#2} \hfill \textcolor{muted}{#4}\\[4pt]
}
% Project entry
\newcommand{\project}[3]{%
  \textbf{#1} \,\textcolor{muted}{\small[#2]} \, --- \, #3 \\[3pt]
}

\begin{document}

% ------------------------------------------------------------------
% Header
% ------------------------------------------------------------------
\begin{center}
    {\Huge\bfseries Za\'u J\'ulio} \\[5pt]
    \small Tech Lead \,|\, Full Stack Software Engineer \,|\, Microservices \& System Design \,|\, AI / ML \\[4pt]
    \footnotesize
    \href{mailto:zaujulio.dev@gmail.com}{zaujulio.dev@gmail.com} \,|\, +55 84 99865-1868 \,|\, Jo\~ao Pessoa, PB, Brazil \\[2pt]
    \href{https://linkedin.com/in/zaujulio}{linkedin.com/in/zaujulio} \,|\,
    \href{https://github.com/ZauJulio}{github.com/ZauJulio} \,|\,
    \href{https://profile.codersrank.io/user/zaujulio}{codersrank.io/@zaujulio} \,|\,
    \href{https://zaujulio.com}{Portfolio: zaujulio.com}
\end{center}

% ------------------------------------------------------------------
% Summary
% ------------------------------------------------------------------
\section{Professional Profile}
Tech Lead and hands-on Full Stack Software Engineer with 5+ years building scalable, high-concurrency systems across the full software development life cycle. Deep expertise in the \textbf{TypeScript / Node.js} ecosystem (\textbf{GraphQL}, Express, NestJS) and in \textbf{Python} for \textbf{AI, Machine Learning, Deep Learning, NLP and time-series} analytics. Designs event-driven \textbf{microservices} backed by job queues (BullMQ, RabbitMQ), models relational and NoSQL data (PostgreSQL, MySQL/MariaDB, MongoDB), and owns delivery end-to-end---from ER modeling and \textbf{C\# / .NET} services to CI/CD, Linux infrastructure and cloud cost optimization. Ranked among the \textbf{top worldwide in GraphQL on CodersRank}. Started engineering before the AI wave and is now fluent at AI-augmented development, leading teams while still shipping production code daily.

% ------------------------------------------------------------------
% Technical Skills (placed early for fast recruiter / ATS scanning)
% ------------------------------------------------------------------
\section{Technical Skills}
\begin{itemize}[leftmargin=14pt, itemsep=2pt, topsep=0pt]
    \item \textbf{Programming Languages:} TypeScript / JavaScript, Python, C\#, Java, C, Bash, SQL.
    \item \textbf{Backend \& Microservices:} Node.js, Express, NestJS, GraphQL, .NET / .NET Core, FastAPI, Django, REST, WebSockets / Socket.io, BullMQ, RabbitMQ.
    \item \textbf{Frontend:} React, Vite, Next.js, Redux, Tailwind CSS, Styled Components, HTML / CSS, SSR, Core Web Vitals.
    \item \textbf{Databases:} PostgreSQL, MySQL / MariaDB, MongoDB, Redis, Data Lakes, ER modeling.
    \item \textbf{AI / Data:} Machine Learning, Deep Learning, NLP, Time Series, Pandas, NumPy, scikit-learn, PyTorch, Matplotlib, Jupyter, R.
    \item \textbf{Infra / DevOps:} Docker, Linux, Shell scripting, CI/CD, AWS, GCP, VPC, CDN, DevSecOps, Monitoring / Observability.
    \item \textbf{Practices:} System design, microservices architecture, SDLC, code review, technical leadership, AI-augmented development (Claude, OpenCode).
\end{itemize}

% ------------------------------------------------------------------
% Experience
% ------------------------------------------------------------------
\section{Experience}

\company{Bitwise Technology}{Sorocaba, SP (Remote)}
\subrole{Tech Lead}{Aug 2025 -- Present}
\begin{itemize}[leftmargin=14pt, itemsep=2pt, topsep=0pt]
    \item Define the engineering roadmap and technical standards for TypeScript microservices and GraphQL schemas, owning system design end-to-end (ER modeling to deployment) while staying hands-on and shipping production code daily.
    \item Drove targeted infrastructure optimization that cut CI/CD build times by 75\% (20 min to under 5) and lowered monthly AWS spend by \textasciitilde80\% (\$120 to \$25), while right-sizing Node.js production services to half the compute and memory footprint with no impact on throughput.
    \item Mentor cross-functional engineers and lead code reviews, instilling a culture of quality, scalability and observability.
\end{itemize}
\vspace{3pt}

\subrole{Full Stack Software Engineer}{Mar 2023 -- Aug 2025}
\begin{itemize}[leftmargin=14pt, itemsep=2pt, topsep=0pt]
    \item Delivered high-availability backends in GraphQL, Node.js, C\#/.NET and MongoDB, modeling complex domain logic and offloading heavy processing to BullMQ and RabbitMQ job queues.
    \item Built fast, SEO-friendly React/Vite/Next.js frontends tuned for SSR and Core Web Vitals, plus the CI/CD pipelines and cloud provisioning that shortened release cycles.
\end{itemize}
\vspace{3pt}

\role{Commcepta}{Full Stack Developer}{Dec 2021 -- Dec 2022}{Curitiba, PR (Remote)}
\begin{itemize}[leftmargin=14pt, itemsep=2pt, topsep=0pt]
    \item Tuned GraphQL queries over a large-scale Data Lake, cutting search latency from \textasciitilde30s to under 6s (up to 50\% faster) and enabling near real-time analytics on Big Data.
    \item Engineered Python pipelines that unified multiple data sources for enterprise decision-making, and hardened a multinational portal for accessibility (a11y) and internationalization (i18n).
\end{itemize}
\vspace{3pt}

\role{Byte Serid\'o Jr -- Junior Enterprise (UFRN)}{Project Director / Front-end Developer}{Jun 2021 -- Nov 2022}{Caic\'o, RN}
\begin{itemize}[leftmargin=14pt, itemsep=2pt, topsep=0pt]
    \item Led the planning and delivery of multiple software projects at the university's junior enterprise, progressing from front-end developer to Project Director.
    \item Mentored and tutored incoming developers, onboarding students on programming fundamentals, engineering best practices and project workflows.
\end{itemize}

% ------------------------------------------------------------------
% Research & Publication
% ------------------------------------------------------------------
\section{Research \& Publication}

\role{LabEPI / UFRN}{AI \& Machine Learning Researcher (Scientific Initiation)}{Aug 2019 -- Sep 2020}{Caic\'o, RN}
\begin{itemize}[leftmargin=14pt, itemsep=2pt, topsep=0pt]
    \item Designed a hybrid classifier combining \textbf{Self-Organizing Maps (SOM)} neural networks with Polynomial Regression for unsupervised anomaly detection in minute-level energy data, improving accuracy over a pure K-Means baseline and reducing false positives.
    \item Optimized AI model generation and reuse, cutting model memory footprint from 2 GB to \textasciitilde200 MB and SOM training time from 10--15 minutes to under 2 minutes.
    \item Authored a peer-reviewed paper published at the Congress of Scientific and Technological Initiation (CICT); project PVF16985-2019, ``Intelligent Management of Energy Consumption'' (GERINCE).
\end{itemize}

% ------------------------------------------------------------------
% Selected Open-Source Projects
% ------------------------------------------------------------------
\section{Selected Open-Source Projects}

\project{FeaturesAnalyzer}{Python}{Time-series analysis and machine-learning toolkit for feature exploration, modeling and forecasting over high-volume datasets.}
\project{ZSOM}{Python}{From-scratch implementation of the Self-Organizing Maps algorithm, powering the unsupervised models from the energy-consumption research.}
\project{weasyprint-pdf-render}{Python, Docker}{High-performance HTML-to-PDF rendering microservice, containerized for horizontal scaling.}
\project{ZeroWhats}{Rust, TypeScript, Tauri}{Privacy-focused WhatsApp Web desktop client built with Tauri and Preact, replacing Electron bloat with native features like app locks and system notifications.}
\project{indago}{TypeScript, SQLite}{Local headless CMS toolkit that transforms Markdown/MDX and JSON content into a typed, searchable content layer with FTS5, zero backend required.}
\vspace{-3pt}

% ------------------------------------------------------------------
% Education
% ------------------------------------------------------------------
\section{Education}
\textbf{UFRN -- Federal University of Rio Grande do Norte} \hfill 2019 -- 2025 \\
B.Sc. in Information Systems --- honors thesis (TCC) graded 10/10 \\[6pt]
\textbf{IMD/UFRN -- Digital Metropolis Institute} \hfill 2018 -- 2019 \\
Technical Degree in Computer Networks

% ------------------------------------------------------------------
% Languages & Awards
% ------------------------------------------------------------------
\section{Languages \& Awards}
\begin{itemize}[leftmargin=14pt, itemsep=2pt, topsep=0pt]
    \item \textbf{CodersRank:} \#1 worldwide in GraphQL (currently \#2); \#1 in Jo\~ao Pessoa and Top 150 in Brazil overall.
    \item \textbf{Awards:} 2nd place --- 1st UFRN Programming Marathon (regional campus); Research Grant PVF16985-2019 (GERINCE).
    \item \textbf{Spoken Languages:} Portuguese (Native), English (Professional Working Proficiency), Spanish (Working Proficiency -- Listening).
\end{itemize}

\end{document}
